%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Chinmaya Kr. Patanaik}
{ \href{mailto:patanaikchinmaya@gmail.com}{patanaikchinmaya@gmail.com} | chinmayakrpatanaik.com | (+91) 8879867656}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Charles University}
\descript{Master's in Computer Science}
\location{Oct 2014 - Aug 2016(Discont.) | Prague, Czech Republic}
\sectionsep

\subsection{National Institute of Technology}
\descript{B.Tech in Computer Science and Engineering}
\location{2007 - June 2011 |  Silchar, India}
%\location{ GPA: 6.22/10}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Website:// \href{http://www.chinmayakrpatanaik.com}{\custombold{Chinmaya Kr. Patanaik }} \\
Github:// \href{https://github.com/pattu777}{\custombold{pattu777}} \\
LinkedIn://  \href{http://www.linkedin.com/in/chinmayakrpatanaik}{\custombold{ChinmayaPatanaik}} \\
Twitter://  \href{https://twitter.com/CPatanaik}{\custombold{@CPatanaik}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Comfortable:}
Python \textbullet{} Django \textbullet{} MySQL \textbullet{} JavaScript \\
\location{Familiar:}
Bootstrap \textbullet{} Jquery \textbullet{} MongoDB  \\
\subsection{Tools and Environment:}
Git \textbullet{} RabbitMQ \textbullet{} Redis \textbullet{} Celery \textbullet{}  Ansible \textbullet{} AWS \textbullet{} Ubuntu\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extras and Awards}
• Created a Slack bot with Node.js to manage expenses - Concur Hackathon, 2015. \\
• Best poster paper at SecurIT 2012 for \textbf{“Obfuscated Malware Detection Using API Call Dependency”}. \\
• Scholarship from Charles Universtiy for 2014-15. \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies}
Football, Cooking, Solving sudokus
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Haptik Infotech}
\descript{| Software Engineer (Backend) }
\location{Sept. 2016 – Present | Mumbai}
\vspace{\topsep}
\begin{tightemize}
\item Built various chatbots(IPL, April fool, Earth hour, Mother's day) at scale in Django which helped in product growth.
\item Designed a distributed real time cricket scores feature using Celery and Redis.
\item Redesigned and built Reminders and Daily Fun channel(Top 2 most engaging features) from ground up.
\item Reduced core reminders mysql table by more than 80\% by using a new cron based approach.
\item Worked with Exotel and Amazon Polly API to manage a distributed reminder call service.
\end{tightemize}
\sectionsep

\runsubsection{Concur Technologies}
\descript{| Software Engineering Intern, ExpenseIT Team }
\location{July 2015 – Jan 2016 | Prague, Czech Republic}
\begin{tightemize}
\item Designed and built a RESTful API service using Spring Boot in the backend and Hawt.io in the frontend.
\item Built a module in PHP(Symfony) to migrate millions of production users from an older version to a newer version of our product.
\end{tightemize}
\sectionsep

\runsubsection{Xervmon}
\descript{| Software Engineer }
\location{August 2013 – August 2014 | Bengaluru, India}
\begin{tightemize}
\item Redesigned the cloud deployment engine in Python and achieved upto 70\% improvement by using a distributed message queue(Gearman).
\item Integrated various cloud services(Amazon AWS, DigitalOcean, Rackspace) via their Python bindings into the core engine.
\item Managed and configured the back-end infrastructure using Ansible.
\end{tightemize}
\sectionsep

\runsubsection{Indian Institute of Technology}
\descript{| Junior Project Fellow}
\location{June 2011 – August 2012 | Guwahati, India}
\begin{tightemize}
\item Worked on various aspects of system security such as reverse engineering worms, static and dynamic analysis of malwares etc.
\item Explored some of the security threats posed by USB HID(Teensy++) devices.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Ansible Django}
\descript{| Ansible playbooks to deploy a Django project on a remote server}
\begin{tightemize}
\item Installing necessary packages and setting up MySQL database.
\item Configuring Gunicorn and Nginx.
\end{tightemize}
Github Repo - \href{https://www.github.com/pattu777/Ansible-Django}{\custombold{https://www.github.com/pattu777/Ansible-Django/}}
\sectionsep


\runsubsection{Lucy}
\descript{| A CLI tool to generate software license}
\begin{tightemize}
\item Written in Python.
\item Uses Github v3 API to create license files.
\end{tightemize}
Github Repo - \href{https://www.github.com/pattu777/Lucy/}{\custombold{https://www.github.com/pattu777/Lucy/}}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
